Designing an Agent for an Active Guidance System for Object Search

### 2018-11-21 paper.tex
Edits, updated simulation figure. Added new relevant work. Can perhaps compare system to these results

\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable sufferers to lead more normal and independent lives. Modern improvements to mobile computing and image processing techniques have provided researchers with new and exciting tools to solve this problem.

The ActiVis project will contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input. The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop} instead of a electro-mechanical servo. This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

The goal of ActiVis is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what the it is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action our agent (the guidance system in this case) takes when it finds itself in any state.

@@

\begin{itemize}
  \item a policy-driven human controller that can drive a user towards a point in space,
  \item an MDP model that understands the spatial relationship between objects that is based on real data and
  \item experiments that prove the effectiveness of the current system implementation.
\end{itemize}

@@

As shown here, much research has been performed on object recognition and guidance towards an object once detected. However, work on active object search is harder to come by. Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active,bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search. With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI\@.

@@

\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object\textbackslash{}destination and then guide the user to it. A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
  \caption{An example of a guidance strategy the MDP will generate. }\label{fig:route-example}
\end{figure}

@@

The reward function was crafted by hand and the parameters were empirically selected. The function values can be found in Table~\ref{tab:rewards}. $R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{max}$) or when it wants to search in a site that has been searched already ($v = true$). Conversely, it gives a significant positive reward when the target object is found.

\begin{table}
  \centering
  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
  \begin{tabular}{ll}
    \toprule
    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
    $r(n >= n_{max})$ & -10 \\ \midrule
    $r(v = true)$  & -10 \\ \midrule
    $r(o = o_{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

We set the model to track a maximum of of 9 steps to the target, with 9 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}). A search can take longer than 9 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function. The MDP therefore has a total of 144 reachable states ($n_{states}=8\times9\times2$).

@@

\begin{table}
  \centering
  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant.}\label{tab:results-full}
  \begin{tabular}{cc|cc|cc}
    \toprule
    \multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 &			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 & 5.4 & 29 & 22 \\ \midrule
    s2 & 79 & 6.7 & 4.8 & 34 & 5.1 \\ \midrule
    s3 & 91 & 6.3 & 4.9 & 31 & 21 \\ \midrule
    s4 & 79 & 6.7 & 4.3 & 37 & 5.6 \\ \midrule
    s5 & 76 & 7.2 & 4.9 & 33 & 14 \\ \midrule
    s6 & 60 & 8.2 & 5.4 & 24 & 10 \\ \midrule
    s7 & 86 & 8.5 & 5.8 & 31 & 16 \\ \midrule
    s8 & 88 & 5.1 & 4.0 & 39 & 21 \\ \midrule
    s9 & 98 & 7.2 & 5.4 & 39 & 18 \\ \midrule
    s10 & 67 & 6.6 & 5.4 & 26 & 12 \\ \midrule\midrule
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\noindent It is estimated that there are 440 million people worldwide that live with mild to severe visual impairments or total blindness~\cite{bourne2017magnitude} and significant effort is being made to enable these people to lead more normal and independent lives. Modern improvements to mobile computing power and image processing techniques have provided researchers with new and powerful tools to solve this problem. The ActiVis project aims to contribute to this effort by delivering an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment with minimal user input. The proposed system implements ideas from the field of active vision, but places a human in the control loop, pictured in Figure~\ref{fig:control-loop}, instead of a electro-mechanical servo. %This project expands upon concepts originally proposed in~\cite{bellotto2013} and~\cite{lock2017portable}.

The goal of the ActiVis system is to understand the user's surroundings and determine what the next best course of action is to reach the target location based on what is currently within view and what has been observed in the past. We trained a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action the agent (the guidance system in this case) takes when it finds itself within some state.

@@

\begin{itemize}
  \item a policy-driven human controller that can drive a user towards a point in space,
  \item a data-based MDP model that understands the spatial relationship between objects and
  \item experiments that prove the effectiveness of the system implementation.
\end{itemize}

@@

Researchers have begun implementing active search and perception~\cite{aloimonos2013active} strategies in robots (CITE) and image classifiers (CITE) in an attempt to optimise their classification and planning tasks by exploiting the structured nature of human object placements.

In (CITE CLASSIFIER), the authors implemented an active search strategy for classifying objects within cluttered images. Their approaches use different methods, but both involve using a model to generate windows of interest to submit to a classifier for classification. The size and locations of the windows within the image are generated using the spatial relationship between objects, taken from the SUNCG and PASCAL datasets, and are iteratively changed based on the output from the respective models. The advantage of their approaches over their contemporaries is that far fewer windows are generated and submitted to the classifier, resulting in lower object classification times. They also report comparable accuracy when compared to their contemporaries.

Similarly, roboticists have moved to incorporate similar strategies on robotic platforms to improve autonomous object search, manipulation and localisation tasks. The authors in (CITE A* PAPER) developed a planning algorithm that allows a robotic manipulator to select an object to move that optimally executes an object search or exploration task in a cluttered environment. In (CITE MDP ROBOT), the authors implemented an MDP that generates the optimal search strategy to find an object in a room over a belief state of object positions and configurations. However, the authors trained their MDP using a custom object-placement and configuration probabilities and have shown that the results are sensitive to changes within this distribution.

In all, much research has been conducted on object recognition and guidance towards an object once detected, as well as active vision within image classifiers and robotic systems. However, work on active object search and guidance with a human is harder to come by. In this work we attempt to implement an active vision guidance system with a human in the loop~\cite{bellotto2013,lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search. With this, we hope to make the searching process less random and move towards a more natural and efficient object searching process to the benefit of the VI\@.

@@

\noindent The ActiVis project's goal is to deliver a stand-alone system that only requires a VI user's input for selecting a target object/destination and then guide the user to it. A complete system diagram is given is Figure~\ref{fig:control-loop} and consists of a number of elements.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/office_desk_example.png}
  \caption{An example of a guidance strategy the MDP generates. }\label{fig:route-example}
\end{figure}

@@

The reward function was crafted by hand and the parameters were empirically selected. The function values can be found in Table~\ref{tab:rewards}. $R$ punishes the agent for every step it takes where it does not find the target object and the negative reward is increased if the agent is taking too long to find the target ($n > n_{\max}$) or when it wants to search in a site that has been searched already ($v = true$). Conversely, it gives a significant positive reward when the target object is found.

\begin{table}
  \centering
  \caption{The reward functions for the MDP.\ }\label{tab:rewards}
  \begin{tabular}{ll}
    \toprule
    $r(s, s'), s\in\mathbf{S}$ & -1  \\ \midrule
    $r(n > n_{\max})$ & -10 \\ \midrule
    $r(v = true)$  & -10 \\ \midrule
    $r(o = o_{target})$ & 10000 \\ \midrule
    \bottomrule
  \end{tabular}
\end{table}

@@

We set the model to track a maximum of of 11 (inclusive) steps to the target, with 11 being the longest possible route on the grid (more details about the grid are in Section~\ref{sec:system-implementation}). A search can take longer than 11 steps, but the MDP considers anything greater than 9 steps as the maximum, which is convenient for keeping a manageable state-space and a simple reward function. The MDP therefore has a total of 144 reachable states ($n_{states}=8\times9\times2$).

@@

\begin{table}
  \centering
  \caption{A table containing the results for the TAR, number of steps and time to target means ($\mu$) and standard deviations ($\sigma$) for each individual participant.}\label{tab:results-full}
  \begin{tabular}{cccc}
    \toprule
    Participant & TAR [\%] & Num. Steps & Time [s] \\ \midrule
    %\multirow{2}{*}{Participant} & \multirow{2}{*}{TAR [\%]} & \multicolumn{2}{c|}{Num. Steps} & \multicolumn{2}{c}{Time [s]} \\ 
				 %&			     & $\mu$ & $\sigma$		       & $\mu$ & $\sigma$  \\ \midrule
    s1 & 94 & 7.2 $\pm$ 5.4 & 29 $\pm$ 22 \\ \midrule
    s2 & 79 & 6.7 $\pm$ 4.8 & 34 $\pm$ 5.1 \\ \midrule
    s3 & 91 & 6.3 $\pm$ 4.9 & 31 $\pm$ 21 \\ \midrule
    s4 & 79 & 6.7 $\pm$ 4.3 & 37 $\pm$ 5.6 \\ \midrule
    s5 & 76 & 7.2 $\pm$ 4.9 & 33 $\pm$ 14 \\ \midrule
    s6 & 60 & 8.2 $\pm$ 5.4 & 24 $\pm$ 10 \\ \midrule
    s7 & 86 & 8.5 $\pm$ 5.8 & 31 $\pm$ 16 \\ \midrule
    s8 & 88 & 5.1 $\pm$ 4.0 & 39 $\pm$ 21 \\ \midrule
    s9 & 98 & 7.2 $\pm$ 5.4 & 39 $\pm$ 18 \\ \midrule
    s10 & 67 & 6.6 $\pm$ 5.4 & 26 $\pm$ 12 \\ \midrule
    \bottomrule                    
  \end{tabular}                    
\end{table}
